---
title: "Lucas Kantorowski"
format: 
  dashboard:
    orientation: columns
    theme: Minty
    nav-buttons:
      - icon: github
        href: https://github.com/LKantoro/lab-3
        aria-label: GitHub
      - icon: linkedin
        href: https://www.linkedin.com/in/lucas-kantorowski/
        aria-label: LinkedIn
server: shiny        
logo: images/wellcomelogo.png
logo-alt: Wellcome Organization Logo
---

```{r}
#| context: setup
#| label: load-packages
#| message: false

library(tidyverse)
library(gt)
library(dplyr)
library(leaflet)
library(sf)
library(scales)
library(plotly)
library(readxl)
library(bslib)
library(bsicons)
library(shiny)
```


```{r}
#| context: setup
#| label: read-in-wellcome-data

wgm2018_crosstab = read_excel(here::here("data", "wgm2018-dataset-crosstabs-all-countries.xlsx"), sheet = 1)

wgm2018_full = read_excel(here::here("data", "wgm2018-dataset-crosstabs-all-countries.xlsx"), sheet = 2)

wgm2018_dict = read_excel(here::here("data", "wgm2018-dataset-crosstabs-all-countries.xlsx"), sheet = 3)
```

```{r}
#| context: setup
#| label: country_label_prep

#creating string based on list provided
countriesstringsplit = str_split(wgm2018_dict[1,3], ',')

#changing the vector into a df and eliminating the last row, which was blank
countriesdf = as.data.frame(countriesstringsplit, col.names = c("country")) %>%
  filter(!row_number() %in% c(145))

#creating a two column data frame about the '=' and changing the code to numeric
countriesdf = countriesdf %>% 
  separate_wider_delim(country, delim = "=", 
                       names = c("country_code", "country_name")) %>% 
  mutate(country_code = as.numeric(country_code))
```

```{r}
#| context: setup
#| label: region_label_prep

#similar process for splitting regions, as was done above for countries

regionsstringsplit = str_split(wgm2018_dict[57,3], ',')

regionsdf = as.data.frame(regionsstringsplit, col.names = c("region")) %>%
  filter(!row_number() %in% c(20))

regionsdf = regionsdf %>% 
  separate_wider_delim(region, delim = "=", 
                       names =c("region_code", "region_name")) %>% 
  mutate(region_code = as.numeric(region_code))


#creating a new column for world region to be used to split the graph

regionsdf = regionsdf %>% mutate('map_region' = case_when(
          region_code %in% c(9,10,11,12, 18) ~ 'Asia and Australia',
          region_code %in% c(1,2,4,5) ~ 'Sub-Saharan Africa',
          region_code %in% c(6,7,8) ~ 'Americas',
          region_code %in% c(15,16,17) ~ 'Europe',
          region_code %in% c(3,13) ~ 'Middle East and North Africa',
          region_code == 14 ~ 'Former Soviet Union',
          region_code == 0 ~ 'Not Assigned'))
```

```{r}
#| context: setup
#| label: full_data_with_countries_and_regions

#merging to create full dataset to use in visuals
wgm2018_full_new1 = left_join(wgm2018_full, countriesdf, 
                              by = join_by(WP5 == country_code))

wgm2018_full_new2 = left_join(wgm2018_full_new1, regionsdf, 
                              by = join_by(Regions_Report == region_code))

countries_and_regions = wgm2018_full_new2 %>% 
  select(country_name, region_name, map_region) %>% distinct()

```



```{r}
#| context: setup
#| label: chloropleth_prep_1

#finding country geometries: https://r-graph-gallery.com/183-choropleth-map-with-leaflet.html

#download.file(
##  "https://raw.githubusercontent.com/holtzy/R-graph-gallery/master/DATA/world_shape_file.zip",
#  destfile = "data/world_shape_file.zip"
#)

#system("unzip DATA/world_shape_file.zip")

world_sf <- read_sf(paste0(
  getwd(), "/data/world_shape_file/",
  "TM_WORLD_BORDERS_SIMPL-0.3.shp"
))
```

```{r}
#| context: setup
#| label: chloropleth_prep_2


country_counts = wgm2018_full_new2 %>% 
  group_by(country_name) %>% 
  summarise(total_count = n()) %>%
  rename('total_surveyed' = total_count)

#finding the count of people who are knowledgeable about science
trust_scientists_counts = wgm2018_full_new2 %>% 
  filter(Q11C %in% c('1', '2')) %>%
  group_by(country_name, map_region) %>% 
  summarise(total_trust = n()) 


#finding percent of people who are knowledgeable about science
percent_trust = inner_join(country_counts, trust_scientists_counts, 
                             by = join_by(country_name == country_name))


percent_trust$perc_trust = 
  round(percent_trust$total_trust/percent_trust$total_surveyed * 100,2)


#joining country geometries and overall data frame together
chloroplethdf = right_join(percent_trust, world_sf, 
                           by = join_by(country_name == NAME))

```


```{r}
#| context: setup
#| label: chloropleth_prep_3


#converting data.frame to sf for graphing using leaflet: https://r-spatial.github.io/sf/reference/sf.html
chloroplethdf = st_sf(chloroplethdf)
```



# Science vs. Vaccines

## {.sidebar width="200px"}

```{r}
#| context: setup

selectInput('valuecard1', label = 'Valuecard 1', 
            choice = c('More About Science', 
                       'More About Disease',
                       'Diseases a Part of Science', 
                       'Science at Primary School', 
                       'Science at Secondary School',
                       'Science at College/University'),
            multiple = FALSE, selected = 'More About Science')

selectInput('valuecard2', label = 'Valuecard 2', 
            choice = c('More About Science', 
                       'More About Disease',
                       'Diseases a Part of Science', 
                       'Science at Primary School', 
                       'Science at Secondary School',
                       'Science at College/University'),
            multiple = FALSE, selected = 'More About Disease')

selectInput('valuecard3', label = 'Valuecard 3', 
            choice = c('More About Science', 
                       'More About Disease',
                       'Diseases a Part of Science', 
                       'Science at Primary School', 
                       'Science at Secondary School',
                       'Science at College/University'),
            multiple = FALSE, selected = 'Diseases a Part of Science')
```


## Column - Plots {width="60%"}

### Row {height="75%"}

```{r}
#| label: plotly_prep_1

#finding the count of surveyed people
country_counts = wgm2018_full_new2 %>% 
  group_by(country_name) %>% 
  summarise(total_count = n()) %>%
  rename('total_surveyed' = total_count)

#finding the count of people who think vaccines are effective
vaccine_effective_counts = wgm2018_full_new2 %>%
  filter(Q26 %in% c('1'), map_region != 'Not Assigned') %>%
  group_by(country_name, map_region) %>% 
  summarise(total_effective = n())
  

#finding the count of people who are knowledgeable about science
know_science_counts = wgm2018_full_new2 %>% 
  filter(Q1 %in% c('1', '2'), map_region != 'Not Assigned') %>%
  group_by(country_name, map_region) %>% 
  summarise(total_science = n()) 

```

```{r}
#| label: plotly_prep_2


#finding percent of people who think vaccines are effective
percent_effective = inner_join(country_counts, vaccine_effective_counts, 
                               by = join_by(country_name == country_name))

percent_effective$percent_eff = 
  percent_effective$total_effective/percent_effective$total_surveyed

#finding percent of people who are knowledgeable about science
percent_science = inner_join(country_counts, know_science_counts, 
                             by = join_by(country_name == country_name))

#finding proportion of people who are knowledgeable about science
percent_science$prop_sci = 
  percent_science$total_science/percent_science$total_surveyed


#joining effective counts with safe counts
percent_effective_and_science = left_join(percent_effective, percent_science, 
                                       by = join_by(country_name==country_name))


#rounding to 2 decimal places for cleanliness
percent_effective_and_science = percent_effective_and_science %>% 
  mutate(percent_eff = round(percent_eff, 2), prop_sci = round(prop_sci, 2))



```

::: {.card title="Belief Vaccines are Effective vs. Understanding of Science"}

```{r}
#| label: plotly_graph

#scatterplot of vaccination rates vs science

plot_ly(data = percent_effective_and_science, 
        x = ~prop_sci, y = ~percent_eff, 
        type = "scatter", mode = "markers", text = ~country_name, 
        color = ~map_region.x) %>%
  layout(plot_bgcolor='white',
    xaxis = list(range = list(0, 1), tickformat = ".0%", 
                 title = "'Strong' or 'Some' Knowledge of Science"),
    yaxis = list(range = list(0, 1), tickformat = ".0%",
                 title = ""), 
    legend = list(x = 0.85, y = 0.04, bordercolor = 'black',
                       borderwidth = 2, font = list(size = 10))) %>%
  add_trace(showlegend = FALSE, hovertemplate = 'Knowledge of Science: %{x} 
Vaccine Effectiveness: %{y}
%{text}')
```

:::


### Row {height="25%"}


```{r}
#| context: setup

uiOutput('myvaluebox1')
```


```{r}
#| context: setup

uiOutput('myvaluebox2')
```

```{r}
#| context: setup

uiOutput('myvaluebox3')
```


```{r}
#| context: setup
#| label: valueboxes_prep

want_to_know_more_science = wgm2018_full_new2 %>% 
  count(Q8) %>% mutate(prop = prop.table(n)) %>% 
  filter(Q8 == '1') %>% 
  select(prop)


want_to_know_more_disease = wgm2018_full_new2 %>% 
  count(Q9) %>% mutate(prop = prop.table(n)) %>% 
  filter(Q9 == '1') %>% 
  select(prop)

disease_part_of_science = wgm2018_full_new2 %>% 
  count(Q3) %>% mutate(prop = prop.table(n)) %>% 
  filter(Q3 == '1') %>% 
  select(prop)


science_primary_school = wgm2018_full_new2 %>% 
  count(Q5A) %>% mutate(prop = prop.table(n)) %>% 
  filter(Q5A == '1') %>% 
  select(prop)

science_secondary_school = wgm2018_full_new2 %>% 
  count(Q5B) %>% mutate(prop = prop.table(n)) %>% 
  filter(Q5B == '1') %>% 
  select(prop)

science_college = wgm2018_full_new2 %>% 
  count(Q5C) %>% mutate(prop = prop.table(n)) %>% 
  filter(Q5C == '1') %>% 
  select(prop)


```


```{r}
#| context: server

#changing font size of valuebox text: 
#https://www.edureka.co/community/32147/change-font-size-of-valuebox-shiny-r





output$myvaluebox1 <- renderUI({
  
  if (input$valuecard1 == 'More About Science')
    v = value_box(
      theme = "info",
      title = "Want To Learn More About Science",
      value = tags$p(paste(round(want_to_know_more_science * 100,0), '%'),
                     style = "font-size: 300%;")
      )
 
  
  if (input$valuecard1 == 'More About Disease')
    v = value_box(
      theme = "info",
      title = "Want To Learn More About Disease",
      value = tags$p(paste(round(want_to_know_more_disease * 100,0), '%'),
                     style = "font-size: 300%;"),
      showcase_layout = showcase_top_right(max_height = "100px"))
  
  if (input$valuecard1 == 'Diseases a Part of Science')
    v = value_box(
      theme = "info",
      title = "Believe Diseases are a Part of Science",
      value = tags$p(paste(round(disease_part_of_science * 100,0), '%'),
                     style = "font-size: 300%;")
      )
 
  
  if (input$valuecard1 == 'Science at Primary School')
    v = value_box(
      theme = "info",
      title = "Learned About Science at Primary School",
      value = tags$p(paste(round(science_primary_school * 100,0), '%'),
                     style = "font-size: 300%;"),
      showcase_layout = showcase_top_right(max_height = "100px"))
  
  if (input$valuecard1 == 'Science at Secondary School')
    v = value_box(
      theme = "info",
      title = "Learned About Science at Secondary School",
      value = tags$p(paste(round(science_secondary_school * 100,0), '%'),
                     style = "font-size: 300%;")
      )
 
  
  if (input$valuecard1 == 'Science at College/University')
    v = value_box(
      theme = "info",
      title = "Learned About Science at College/University",
      value = tags$p(paste(round(science_college * 100,0), '%'),
                     style = "font-size: 300%;"),
      showcase_layout = showcase_top_right(max_height = "100px"))
    
  v
  
})



output$myvaluebox2 <- renderUI({
  
  if (input$valuecard2 == 'More About Science')
    v = value_box(
      theme = "success",
      title = "Want To Learn More About Science",
      value = tags$p(paste(round(want_to_know_more_science * 100,0), '%'),
                     style = "font-size: 300%;")
      )
 
  
  if (input$valuecard2 == 'More About Disease')
    v = value_box(
      theme = "success",
      title = "Want To Learn More About Disease",
      value = tags$p(paste(round(want_to_know_more_disease * 100,0), '%'),
                     style = "font-size: 300%;"),
      showcase_layout = showcase_top_right(max_height = "100px"))
  
  if (input$valuecard2 == 'Diseases a Part of Science')
    v = value_box(
      theme = "success",
      title = "Believe Diseases are a Part of Science",
      value = tags$p(paste(round(disease_part_of_science * 100,0), '%'),
                     style = "font-size: 300%;")
      )
 
  
  if (input$valuecard2 == 'Science at Primary School')
    v = value_box(
      theme = "success",
      title = "Learned About Science at Primary School",
      value = tags$p(paste(round(science_primary_school * 100,0), '%'),
                     style = "font-size: 300%;"),
      showcase_layout = showcase_top_right(max_height = "100px"))
  
  if (input$valuecard2 == 'Science at Secondary School')
    v = value_box(
      theme = "success",
      title = "Learned About Science at Secondary School",
      value = tags$p(paste(round(science_secondary_school * 100,0), '%'),
                     style = "font-size: 300%;")
      )
 
  
  if (input$valuecard2 == 'Science at College/University')
    v = value_box(
      theme = "success",
      title = "Learned About Science at College/University",
      value = tags$p(paste(round(science_college * 100,0), '%'),
                     style = "font-size: 300%;"),
      showcase_layout = showcase_top_right(max_height = "100px"))
    
  v
  
})


output$myvaluebox3 <- renderUI({
  
  if (input$valuecard3 == 'More About Science')
    v = value_box(
      theme = "light",
      title = "Want To Learn More About Science",
      value = tags$p(paste(round(want_to_know_more_science * 100,0), '%'),
                     style = "font-size: 300%;")
      )
 
  
  if (input$valuecard3 == 'More About Disease')
    v = value_box(
      theme = "light",
      title = "Want To Learn More About Disease",
      value = tags$p(paste(round(want_to_know_more_disease * 100,0), '%'),
                     style = "font-size: 300%;"),
      showcase_layout = showcase_top_right(max_height = "100px"))
  
  if (input$valuecard3 == 'Diseases a Part of Science')
    v = value_box(
      theme = "light",
      title = "Believe Diseases are a Part of Science",
      value = tags$p(paste(round(disease_part_of_science * 100,0), '%'),
                     style = "font-size: 300%;")
      )
 
  
  if (input$valuecard3 == 'Science at Primary School')
    v = value_box(
      theme = "light",
      title = "Learned About Science at Primary School",
      value = tags$p(paste(round(science_primary_school * 100,0), '%'),
                     style = "font-size: 300%;"),
      showcase_layout = showcase_top_right(max_height = "100px"))
  
  if (input$valuecard3 == 'Science at Secondary School')
    v = value_box(
      theme = "light",
      title = "Learned About Science at Secondary School",
      value = tags$p(paste(round(science_secondary_school * 100,0), '%'),
                     style = "font-size: 300%;")
      )
 
  
  if (input$valuecard3 == 'Science at College/University')
    v = value_box(
      theme = "light",
      title = "Learned About Science at College/University",
      value = tags$p(paste(round(science_college * 100,0), '%'),
                     style = "font-size: 300%;"),
      showcase_layout = showcase_top_right(max_height = "100px"))
    
  v
  
})

```


## Column - Medals by year {width="40%"}

### Row - Vaccines {.tabset height="75%"}

::: {.card title="Belief in Vaccine Effectiveness"}

```{r}
#| label: dotplot_1

percent_effective %>% ggplot(aes(x = percent_eff, fill = map_region, 
                              color = map_region)) +
  geom_dotplot(binwidth = .01) + 
  facet_grid(rows = vars(map_region), axis.labels = "margins") +
  labs(x = "", y = "", fill = "",
       title = 
         "People Who 'Agreed' or 'Strongly Agreed' Vaccines Are Effective") +
  geom_text(aes(x = .5, y = .8, label = map_region)) +
  theme_light() + 
  theme(strip.text = element_blank(), legend.position = "none", 
        panel.grid.minor = element_blank(), panel.grid.major =element_blank(),
        plot.title.position = "plot", axis.text.y = element_blank(), 
        axis.ticks.y = element_blank()) +
  scale_x_continuous(labels = scales::percent, limits = c(0,1))
```

:::

::: {.card title="Knowledge of Science"}

```{r}
#| label: dotplot_2

percent_science %>% ggplot(aes(x = prop_sci, fill = map_region, 
                              color = map_region)) +
  geom_dotplot(binwidth = .01) + 
  facet_grid(rows = vars(map_region), axis.labels = "margins") +
  labs(x = "", y = "", fill = "",
       title = "People Who Claim 'A lot' or 'Some' Understanding of Science") +
  geom_text(aes(x = .5, y = .8, label = map_region)) +
  theme_light() + 
  theme(strip.text = element_blank(), legend.position = "none", 
        panel.grid.minor = element_blank(), panel.grid.major = element_blank(),
        plot.title.position = "plot", axis.text.y = element_blank(), 
        axis.ticks.y = element_blank()) +
  scale_x_continuous(labels = scales::percent, limits = c(0,1))
```

:::


### Row - Tables {.tabset height="25%"}

::: {.card title="Vaccine Safety Beliefs Top 30"}

```{r}
#| label: table_1

#table of safe vaccination rates (in percents)

top30rate = wgm2018_full_new2 %>% 
  group_by(country_name, Q25) %>% 
  summarize(total_count = n()) %>%
  pivot_wider(names_from = 'Q25', values_from = 'total_count') %>%
  select(country_name, '1', '2', '3', '4', '5') %>%
  mutate(total = sum(c_across(1:5))) %>% 
  mutate(across(1:5, ~ . / total)) %>%
  rename("Strongly_Agree" = '1', "Somewhat_Agree" = '2', 
         "Neither" = '3', "Somewhat_Disagree" = '4',
         "Strongly_Disagree" = '5') %>% 
  arrange(desc(Strongly_Agree)) 


top30rate %>% select(!total) %>%
  rename("Country" = "country_name",
         "Strongly Agree" = "Strongly_Agree", 
         "Somewhat Agree" = 'Somewhat_Agree',
         "Somewhat Disagree" = 'Somewhat_Disagree',
         "Strongly Disagree" = 'Strongly_Disagree') %>% 
  ungroup() %>%
  slice_head(n = 30) %>%
  gt() %>% 
  cols_align(align = "left", columns = Country) %>% 
  data_color(
    method = "numeric",
    palette = "BuGn"
  ) %>% fmt_percent(c('Strongly Agree', 'Somewhat Agree', 'Neither',
                      'Somewhat Disagree', 'Strongly Disagree'))
```
:::

::: {.card title="Vaccine Safety Beliefs Bottom 30"}

```{r}
#| label: table_2

#table of safe vaccination rates (in percents)

  
bottom30rate = wgm2018_full_new2 %>% 
  group_by(country_name, Q25) %>% 
  summarize(total_count = n()) %>%
  pivot_wider(names_from = 'Q25', values_from = 'total_count') %>%
  select(country_name, '1', '2', '3', '4', '5') %>%
  mutate(total = sum(c_across(1:5))) %>% 
  mutate(across(1:5, ~ . / total)) %>%
  rename("Strongly_Agree" = '1', "Somewhat_Agree" = '2', 
         "Neither" = '3', "Somewhat_Disagree" = '4',
         "Strongly_Disagree" = '5') %>% 
  arrange(desc(Strongly_Disagree))


bottom30rate %>% select(!total) %>%
  rename("Country" = "country_name",
         "Strongly Agree" = "Strongly_Agree", 
         "Somewhat Agree" = 'Somewhat_Agree',
         "Somewhat Disagree" = 'Somewhat_Disagree',
         "Strongly Disagree" = 'Strongly_Disagree') %>% 
  ungroup() %>% 
  slice_head(n = 30) %>%
  gt() %>% 
  cols_align(align = "left", columns = Country) %>% 
  data_color(
    method = "numeric",
    palette = "BuGn"
  ) %>% fmt_percent(c('Strongly Agree', 'Somewhat Agree', 'Neither',
                      'Somewhat Disagree', 'Strongly Disagree'))

```
:::


# Trust in Scientists

## {.sidebar width="200px"}

```{r}
#| context: setup


#Create global sidebars by adding the .sidebar class to level 1 headings. Sidebars can include code cells as well as images, narrative, and links.



sliderInput('numBins', 'Number of Bins', 
            min=2, max=11,
            value=11, 
            step=1, round=0)
br()
p()

```


## Column - Plots {width="60%"}

::: {.card title="Percentage of Population Who Have High Trust in Scientists"}


```{r}
#| context: setup

#https://rstudio.github.io/leaflet/articles/shiny.html
leafletOutput('mymap')
```

```{r}
#| context: server
#| label: chloropleth1


#creating bins for coloring
colorpal <- reactive({
  colorBin("Spectral", reverse = FALSE, domain = chloroplethdf$perc_trust,
               bins = seq(0,100,length.out = input$numBins))
})


#only include aspects of the map that wont need to be changed dynamically
output$mymap <- renderLeaflet({ 
  
  pal <- colorpal()
  
  leaflet(chloroplethdf) %>% addTiles()  %>%
    setView(lng = 0, lat = 0, zoom = 2) %>%
    addPolygons(weight = .2, opacity = 1,
                fillColor = ~pal(perc_trust), 
                popup = ~paste(country_name, ":",perc_trust, '%'), 
                label = ~paste(country_name, ":",perc_trust, '%'), 
                stroke = FALSE) %>%
    addLegend(pal = pal, title = "",
              values = ~perc_trust, position = "bottomleft",            
              labFormat = labelFormat(suffix = "%"))
})

#aspects of map that will be changed dynamically

observe({
  
  pal <- colorpal()

  leafletProxy("mymap", data = chloroplethdf)  %>% 
    clearShapes() %>%
    addPolygons(weight = .2, opacity = 1,
                fillColor = ~pal(perc_trust), 
                popup = ~paste(country_name, ":",perc_trust, '%'), 
                label = ~paste(country_name, ":",perc_trust, '%'), 
                stroke = FALSE)
    
})

observe({
    pal <- colorpal()

    leafletProxy("mymap", data = chloroplethdf) %>% 
    clearControls() %>%
    addLegend(pal = pal, title = "",
              values = ~perc_trust, position = "bottomleft",            
              labFormat = labelFormat(suffix = "%"))
    
  })
```

:::


## Column - Medals by year {width="40%"}

### Row - Valueboxes {height="30%"}

```{r}
#| label: valuebox_prep

#Q11C, trust in scientists

#percent of religious people who trust scientists
religious_trust_science = wgm2018_full_new2 %>% filter(D1 == '1') %>%
  count(Q12) %>% mutate(prop = prop.table(n)) %>%
  filter(Q12 == '1') %>% select(prop)


#percent of non-religious people who trust scientists
non_religious_trust_science = wgm2018_full_new2 %>% filter(D1 == '2') %>%
  count(Q12) %>% mutate(prop = prop.table(n)) %>%
  filter(Q12 == '1') %>% select(prop)

```

::: {.valuebox icon="yin-yang" color="#c3f9de"}
`{r} paste(round(religious_trust_science*100,1),"%")`

of Religious People Have High Trust in Science

:::

::: {.valuebox icon="slash-circle" color="#f2cad2"}
`{r} paste(round(non_religious_trust_science*100,1),"%")`

of Non-Religious People Have High Trust in Science
:::

### Row - Medals By Year {height="70%"}

::: {.card title="Science Belief By Education Level"}


```{r}
#| label: barplot
#barplot in distribution of belief about science by education level

wgm2018_full_new2 %>% filter(Q12 %in% c(1,2,3,4)) %>% 
  filter(Education %in% c(1,2,3)) %>%
  ggplot(aes(x = factor(Education, levels = c('1', '2', '3'), 
                        labels = c('Primary','Secondary', 'Tertiary')),
             fill = factor(Q12, levels = c('4', '3', '2', '1'), 
                           labels = c('None', 'Little', 'Some', 'Strong')))) + 
  geom_bar(position = "fill") +
  scale_y_continuous(labels = scales::percent) +
  labs(x = 'Education Level', y = '', fill = 'Belief Level') +
  theme(legend.position = "right", panel.grid = element_blank(),
        axis.ticks.x = element_blank(), axis.ticks.y = element_blank(),
        plot.title.position = "plot", panel.grid.major = element_blank()) +
  scale_fill_manual(values = c('#f2cad2', '#f5d8e3', '#d3fdef', '#c3f9de')) +
  theme_minimal() +
  theme(panel.grid.minor = element_blank(), panel.grid.major.x =element_blank(),
        panel.grid.major.y =element_blank(), axis.ticks.x = element_blank())

```

:::